\section{Attack Models}\label{sec-attack}

In this section we consider several attack models and discuss how our
design offer protection against these attacks.

\subsection{Server Attack}
The first attack model is server attack. In this attack, the server cannot
be trusted or can be a source of identity of disclosure. Most services logs
the identity of the users with the data submitted through their services.
If the server is malicious, or mandated by someone powerful for disclosure,
privacy of the users are compromised.

First we analyze the payload transmission part of our design against
server attack. We assume that the server can see the packets sent to it,
but does not see the packets in the network before it reaches it. In
other words the server does not control the Internet and cannot perform
traffic analysis on the Internet. Under this assumption, in our One-Way
protocol the sender has the anonymity level of beyond suspicion since
a server cannot infer any identity information from the data packet it
receives. The only linking information is the identity of the network
device (e.g. link layer switch) at the last hop of the route. We assume
the service does not control the Internet, therefore it cannot link
this information back to the sender.

Next we analyze our validation protocol again server attack. Keep in mind,
our validation uses peer network to transmit acknowledgement and control
messages.
Since the server has to run our anonymous validation protocol, it is
consider one of the network peers and therefore it can
find out the users in the peer network, but the server does not know the
original hop count $h$ of the control packets. In addition, any peer can
potentially be connected with any other peers therefore, the sender is
also beyond suspicion in this case.

\subsection{Eavesdrop and Traffic Analysis}

In eavesdrop attack, we assume that the data transmission route is divided
into segments each controlled by a network administrator. An attacker is
able to listen to the traffic of a segment, but cannot eavesdrop
on all the network segments of the route. In other words, the attacker
not have the full view of the entire route, but only a segment.

There are two scenarios. The first scenario is that the sender of the
data does not reside on the network on which the attacker is eavesdropping
and the the level of anonymity for the sender is beyond suspicion. Although
the attacker is able to listen to the traffic to his network, it is
unable to see who the sender is from the other network.

The second scenario is that the sender and the attacker are on the same
network. In this case the attacker is able to analyze the traffic of any
node on the network. In this scenario, our design is unable to protect the
identity of the sender and the level of anonymity is exposed. The way the
attack could get the sender's identity is to compare the incoming and
outgoing traffic for every node in the network. For the nodes that have
outgoing traffic for a specific content without corresponding incoming
traffic is suspected of data originator. Encryption of data on top of our
design can mitigate this attack.
