\documentclass[10pt,conference,letterpaper]{IEEEtran}
\usepackage{times,amsmath,epsfig}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
%\usepackage{epsfig}
\usepackage{color}
\usepackage{amssymb}
%\usepackage{amsmath}
\usepackage{flushend}
\usepackage{cite,float}
\usepackage[normalem]{ulem}
\usepackage{verbatim}
%\usepackage{subfig}
\usepackage{subfigure}

\title{Anonymous Network Protocol for Mobile Participatory Sensing}

\author{
Chih-Jye Wang, Wei-Shinn Ku, John Patrick Wall
% add some space between author names and affils
\vspace{1.6mm}\\
\fontsize{10}{10}\selectfont\itshape
Department of Computer Science and Software Engineering\\
Auburn University, AL, USA\\
\fontsize{9}{9}\selectfont\ttfamily\upshape
\{wangchj, wzk0004, jpw0001\}@auburn.edu\\
}

\begin{document}

\maketitle

\begin{abstract}
In the participatory sensing, users with mobile devices (e.g. cell phones
and location-aware devices) participate in the collection of environmental
information around them and submit the collected data to a central server
for processing and analysis. Identity privacy of mobile users in this model
is a major concern that hinders the adoption of this computing model. In
addition, bandwidth and computing capability are limited for mobile devices.
Unfortunately, most previously proposed work on user anonymity are not
designed specific for mobile environment and thus resource constraint is
not main focus of their solutions.
In this paper, we propose One-way, an anonymous networking protocol designed
with mobile participatory sensing environment in mind. Our protocol utilizes
peer-to-peer network to facilitate anonymous data transmission to protect
sender identity, but the actual data payload are not sent through peers. For
data, we remove sender information and transmission through direct path.
Since the data are not copied to multiple peers, our design consumes less
resources. Our evaluation shows that our approach utilizes less overall
bandwidth with lower transmission latency and more scalable than other
more complex designs.
\end{abstract}

% NOTE keywords are not used for conference papers so do not populate them
\begin{keywords}
ignore
\end{keywords}
%

\input{intro}
\input{rel_works}
\input{protocol}
\input{implement}
\input{attack}
\input{evaluation}
%\section{Query Processing}\label{sec-processing}
%\input{processing}

\section{Future Work}
Future work includes reliability and security of this approach.


%\section{Demonstration}\label{sec-demo}
%\input{demo}

\input{conclusion}

\section*{Acknowledgment}

The heading of the Acknowledgment section and the References section
must not be numbered.

Causal Productions wishes to acknowledge Michael Shell and other
contributors for developing and maintaining the IEEE LaTeX style files
which have been used in the preparation of this template.  To see the
list of contributors, please refer to the top of file IEEETran.cls in
the IEEE LaTeX distribution.

\bibliographystyle{abbrv}
\bibliography{bib}

\end{document}
