\section{Related Works}\label{sec-related-works}
One of the earliest work on anonymous communication is on untraceable
electronic mail by Chaum\cite{DBLP:journals/cacm/Chaum81}. The work proposed
a way of sending an electronic mail to a receiver in which the sender
remain anonymous using one or a series of proxy computers called Mixes.
Chaum's solution relies heavily on public key cryptography in a way that
before forwarding a mail to a mix, the message and the receiver's address
is encrypted using the mix's public key. Upon receiving an electronic
message, the mix extracts the information
and forwards the mail to the intended receiver. In the case of multiple
mixes, the sender performs one public key cryptography for each mixes before
sending a mail to the first mix. The mix then forward it to the next mix
and so on until the mail reaches the receiver. One of the drawback of the
solution proposed in \cite{DBLP:journals/cacm/Chaum81} is scalability since
the senders depend on fixed proxies and if there are not proxies, the
solution will not work. Also multiple public key cryptography is expensive
for mobile devices. Multiple public key is acceptable for small file, but
for large files that need to be broken down and sent with multiple segments,
multiple encryption may not be acceptable.

Another well known research of sender anonymity is the
onion routing\cite{DBLP:conf/uss/DingledineMS04}. The onion routing
follows the similar approach as in \cite{DBLP:journals/cacm/Chaum81} of
using multiple proxies and multiple encryptions. Before sending a file,
the sender selects a number of proxies called onion routers. The selected
routers have no say in the selection process, thus mitigating malicious
node collaboration attack. After selecting the routers, the sender
encrypts its data with the key of the first router, then encrypt the result
of that with the key of the second router, and does the same for all the
routers. Onion routing is robust in terms
of security and can be used in many applications, but it has the same
drawback as in Chaum's approach that it is computationally expensive
because of the multiple encryptions. Our solution does not impose multiple
encryption to the application, but give that choice to the developer
of the application.

Freenet, a distributed anonymous storage system was proposed
in \cite{DBLP:conf/diau/ClarkeSWH00}. The goal of the system is to utilize
the peers in the network for storage and at the same time achieving anonymity
of the author of the files. Freenet utilizes file keys obtained by public
key cryptography and hashing to achieve efficient file storage and searching.
In order to achieve author anonymity, a node on the Freenet sends a file
to a peer, and the peer forwards the file to another peer and so on, much
like the solution in Crowds. Although, the system pertains to file storage,
the technique of utilizing peers to hide the identity of the originator of
a file is useful in our scenario and we take a similar approach with our
data verification of our design.

Crowds\cite{DBLP:journals/cacm/ReiterR99} utilizes peer-to-peer network
to blend the sender into a large number of users (a crowd) so that the
receiver does not know the true identity of the sender.
To send a file, the sender joins a close-by crowd and sends the file to
one of its peers in the crowd called jondo (a short name for John Doe).
When a peer receives a send request, it decides whether to forward the
data to another peer based on the variable $p_f$ that determines the
probability of forwarding the packet.

The closest work to ours is research on privacy for mobile users in sensing
networks \cite{DBLP:conf/percom/HuS10} by Hu and Shahabi. The assumption of the
work is that data collection service providers often log the identity of the
user with the file they submit. The disclosure of this sensitive information
leads to the compromising of user privacy. The solution is to leverage
social network to forward a file to multiple peers before sending it to
the server. Large consumption of network bandwidth is a big disadvantage in
this approach since a file is sent to multiple users, and this concern is
exacerbated in wireless mobile environments where bandwidth is limited.
In our approach, we do not forward the payload of the data to multiple peers,
only the control messages of the data transmission and saves tremendous amount
of bandwidth.