\documentclass[10pt,conference,letterpaper]{IEEEtran}
\usepackage{times,amsmath,epsfig}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{color}
\usepackage{amssymb}
\usepackage{flushend}
\usepackage{cite,float}
\usepackage[normalem]{ulem}
\usepackage{verbatim}
\usepackage{subfigure}

\title{Anonymous Sensory Data Collection for Mobile Participatory Sensing}

\author{
Chih-Jye Wang, Wei-Shinn Ku, John Patrick Wall
% add some space between author names and affils
\vspace{1.6mm}\\
\fontsize{10}{10}\selectfont\itshape
Department of Computer Science and Software Engineering\\
Auburn University, AL, USA 36849\\
\fontsize{9}{9}\selectfont\ttfamily\upshape
\{wangchj, weishinn, jpw0001\}@auburn.edu\\
}

\begin{document}

\maketitle

\begin{abstract}
In participatory sensing, users with mobile devices participate in
the collection of environmental information around them and submit
the collected data to a central server for process and analysis.
Identity privacy of mobile users in this model is a major concern
that hinders the adoption of this data collection model. In
addition, bandwidth and computing capability are limited for
mobile devices. Unfortunately, most previously proposed works on
user anonymity are not designed specific for mobile environments
and thus resource constraint is not the main focus of their
solutions. In this paper, we propose One-way, an anonymous data
sharing protocol designed with mobile participatory sensing
environments in mind. Our method utilizes peer-to-peer network to
facilitate anonymous data transmission to protect sender identity,
but the actual data payload is not sent through peers. For data
packets, we remove sender information and transmission through a
direct path to the server. Since data are not copied to multiple
peers, our design consumes less resources. Our evaluation shows
that our approach utilizes less overall bandwidth with lower
transmission latency and more scalable than other more complex
solutions.
\end{abstract}


\section{Introduction}\label{sec-intro}
\input{intro}

\section{Related Work}\label{sec-related-works}
\input{rel_works}

\section{Anonymous Sensory Data Collection}\label{sec-protocol}
\input{protocol}

\section{Implementation Issues}\label{sec-imp}
\input{implement}

\section{Attack Models}\label{sec-attack}
\input{attack}

\section{Performance Evaluation}\label{sec-evaluation}
\input{evaluation}

\section{Conclusions}\label{sec-conc}
\input{conclusion}

\section*{Acknowledgment}
This research has been funded in part by the National Science
Foundation (NSF) Grants CNS-0831502 (CT) and CNS-0855251 (CRI).

\bibliographystyle{plain}
\bibliography{bib}

\end{document}
